\documentclass{coverletter}

\begin{document}

\name{Harrison Chen}
\contactinfo{New York, NY}{hchen.robotics@gmail.com}{+1(734)968-5295}
\hline{0.5pt}\vspace{10pt}

\today
\\~\\~\\
Dear Hiring Manager,
\\~\\
% Introduction:
% - State the position you're applying
% - Provide brief relevant background and why you're excited for the role
I am writing to express my interest in the Software Engineer II position on the State
Estimation team at Latitude AI. As a robotics software engineer with experience and
interest in mobile autonomous systems, I was eager to apply after discovering this
opportunity on the company's career website. Earlier this month, my team at PDW was
dissolved due to shifting company priorities, and I am now seeking a new role in the
mobile robotics space. I am confident that my technical skills, self-driven mindset, and
career aspirations align well with this position, and I would cherish the opportunity to
contribute to Latitude AI's mission.
\\~\\
% Body:
% - Highlight key skills and experiences that align with job description
% - Add info about measurable impacts if possible
Working on small start-up teams has required me to work on a wide breadth of autonomy
algorithms, but I have specific experiences in deep learning, multi-object tracking, and state estimation that would help me in this role. In my most recent job at PDW, I evaluated stereo depth estimation DNNs like HITNet and Nvidia ESS DNN, optimizing them for Nvidia Jetson while varying file type, precision, input image size, and more. At the end of last year, I trained DNN feature extractor XFeat on a custom dataset, then reconfigured its class implementation to be compatible with training LightGlue, a feature matching network. These tasks provided me with experience in higher-level integration work and lower-level model modification and tuning.
\\~\\
At my prior position with Jugaad Labs, I used CenterTrack, an in-image tracking DNN, to
do multi-object detection. I projected the network's bounding box output into 3D space to
determine object position, which then became measurements for state estimation. In terms
of Bayesian estimation, we used Kalman filters to smooth out predictions for each
object's trajectory, allowing the system to more reliably identify risks and potential
collisions. Additionally, during my Robotics MS, I implemented extended and unscented
Kalman filters, particle filters, and CNNs. Having the opportunity to apply those
learnings in practical work environment has further solidified my proficiency in the
areas of state estimation and deep learning.
\\~\\
% Closing:
% - Reaffirm interest in the role and confidence in your fit
% - Ask discuss qualifications further in an interview
I gravitated to this role for its fit with my mobile robotics experience, but also
because of my affinity for the company. My mom worked for Ford for 20 years, driving me
to grade school in a 1996 Ford Windstar. Latitude AI is a subsidiary of Ford bringing
ADAS technology to its vehicles, so I feel especially invested in its mission statement
and success. Overall, I feel confident that I am a strong fit for this role and well-positioned to
make positive contributions within it. I would love an opportunity to discuss the role
and my qualifications further. Thank you for your consideration, and I look forward to
hearing from you!
\\~\\
Best wishes,
\\
Harrison Chen

\end{document}